\mytitle

### 2017-11-09 paper.tex
nits

\newcommand{\xxx}[0]{\textsc{APUS}\xspace}
\newcommand{\paxos}[0]{\textsc{Paxos}\xspace}
\newcommand{\mytitle}[0]{\textbf {Problems on providing efficient fault 
tolerance to programs}}
\newcommand{\mykeywords}[0]{State Machine Replication, Fault Tolerance, Stable 
and Deterministic Multithreading, Software Reliability}

@@

\subsection*{Issue 1: Poor scalability}
The consensus latency of extant consensus protocols 
is often \emph{scale-limited}: it increases drastically when the number of 
concurrent requests or replicas 
increases~\cite{zookeeper,glendenning2011scalable}.

@@

@@

\subsection*{Issue 2: Hard to use}
Most existing \smr systems are not designed to 
support unmodified server programs. To utilize existing \smr services, 
developers often have to rewrite their code to orchestrate server programs into 
the narrowly defined interfaces provided by these \smr systems. For instance, 
to leverage \zookeeper~\cite{zookeeper}, developers have to shoehorn their 
programs into the file IO interface defined by \zookeeper. As an another 
example, in order to provide fault tolerance to a whole virtual machine, most 
of the existing \smr systems need to modify the hypervisor code which can be 
complex and error-prone.

\subsection*{Issue 3: High Consensus Latency}

>>>>

\newcommand{\xxx}[0]{\textsc{APUS}\xspace}
\newcommand{\paxos}[0]{\textsc{Paxos}\xspace}
\newcommand{\mytitle}[0]{\textbf {Problems on providing efficient fault 
tolerance to server programs}}
\newcommand{\mykeywords}[0]{State Machine Replication, Fault Tolerance, Stable 
and Deterministic Multithreading, Software Reliability}

@@

\subsection*{Issue 1: High Consensus Latency}

\subsection*{Issue 2: Poor scalability}

@@

The consensus latency of extant consensus protocols 
is often \emph{scale-limited}: it increases drastically when the number of 
concurrent requests or replicas 
increases~\cite{zookeeper,glendenning2011scalable}.

@@

\subsection*{Issue 3: Hard to use}
Most existing \smr systems are not designed to 
support unmodified server programs. To utilize existing \smr services, 
developers often have to rewrite their code to orchestrate server programs into 
the narrowly defined interfaces provided by these \smr systems. For instance, 
to leverage \zookeeper~\cite{zookeeper}, developers have to shoehorn their 
programs into the file IO interface defined by \zookeeper. As an another 
example, in order to provide fault tolerance to a whole virtual machine, most 
of the existing \smr systems need to modify the hypervisor code which can be 
complex and error-prone.
